---
title       : "A Fresh Approach" Chapter 6
description : Computing Exercises
attachments :
  slides_link : https://s3.amazonaws.com/assets.datacamp.com/course/teach/slides_example.pdf
---

--- type:NormalExercise lang:r xp:100 skills:1 key:24508ccae0
## Descriptive graphics (should go in an earlier chapter.)

Here is a display constructed using the Current Population Survey wage data, `CPS85`:

*** =pre_exercise_code
```{r}
library(statisticalModeling)
data(CPS85, package = "mosaicData")
gf_boxplot(wage ~ sector + color:sex, data = CPS85)
```

*** =instructions
1. Determine what mode of graphic this is, e.g. 
    - a scatterplot? `gf_point()`
    - a densityplot? `gf_density()`
    - a box-and-whiskers plot? `gf_boxplot()`
2. Read the graphic to determine which variable is playing which role: 
    - x-axis 
    - y-axis 
    - color
3. Construct a command that re-creates the graphic.

*** =sample_code
```{r}
# Fill in the ..blanks..
..plot_mode_fun.. ( ..formula.. , data = CPS85)
```

*** =solution
```{r}
gf_boxplot(wage ~ sector + color:sex, data = CPS85)
```

*** =hint
- It's a box-and-whisker plot.
- `wage` is on the y-axis.
- `sector` is on the x-axis.
- `sex` is shown by color.

*** = sct
```{r}
test_function("gf_boxplot", args = c("formula", "data"), 
              not_called_msg = "It should be a box-and-whiskers plot (`gf_boxplot()`)",
              incorrect_msg = "The arguments should be a formula and `data = CPS85`.")
success_msg("")
```

--- type:NormalExercise lang:r xp:100 skills:1 

## Modeling swim times I

The graphic shows a model of swim times in the `mosaicData::SwimRecords` data.

*** =instructions
1. Look at the graphic to determine which is the response variable and which are the explanatory variables.
2. Use the "shape" of the model to determine which model terms have been included.
3. Build that model.
4. Use `evaluate_model()` to get some examples of model inputs and outputs. By comparing these to the graph you can see if you built the right model.

*** =pre_exercise_code
```{r}
library(statisticalModeling)
library(ggplot2)
data(SwimRecords, package = "mosaicData")
.mod <- lm(time ~ sex + I(0*year), data = SwimRecords)
fmodel(.mod, ~ year + sex) + geom_point(data = SwimRecords, aes(x = year, y = time, color = sex))
```

*** =solution
```{r}
# Build the model
my_model <- lm(time ~ sex, data = SwimRecords)

# Get some examples of model inputs/outputs 
# and compare to the graph
evaluate_model(my_model)
```

*** =sample_code
```{r}
# Build the model
my_model <- lm(.___, data = SwimRecords)

# Get some examples of model inputs/outputs 
# and compare to the graph
evaluate_model(my_model)
```

*** =sct
```{r}
# Final message the student will see upon completing the exercise
success_msg("The model has just sex as an explanatory variable, which is why the lines on the graph are constant for all years.")
```
--- type:NormalExercise lang:r xp:100 skills:1  key:cbf276cdce
## Graphing Models with fmodel()

Given data and a model design, the computer will find the model function and model values for you.  As an example, consider the Current Population Survey  data `mosaicData::CPS85`.  Suppose you want to build a model with `wage` as a response variable and `age` and `sex` as explanatory variables incorporated as main terms.

The two arguments to `lm()` are:

1. the model design, expressed as a formula: `wage` ~ `age` + `sex`.
2. the data to be used: `data = CPS85` 

Once you have built the model, you can graph it. The plot shows one such graph.


*** =instructions
Create a graphics using `fmodel()` that depict `mod1` in each of two ways

- age on the x-axis and sex as color
- sex on the x-axis and age as color

*** =hint
The two arguments to `fmodel()` are

1. The model object itself, in this case `mod1`.
2. A formula describing which roles the explanatory variable will play in the plot, e.g. `~ age + sex` or `~ sex + age`.

*** =pre_exercise_code
```{r}
library(statisticalModeling)
data(CPS85, package = "mosaicData")
mod1 <- lm( wage ~ 1 + age + sex, data = CPS85)
fmodel(mod1)
```

*** =sample_code
```{r}
# Construct the model
mod1 <- lm( wage ~ 1 + age + sex, data = CPS85)

# Make a graphic of mod1 with age on the x-axis and sex as color.
fmodel(mod1, ~ .___ + .___)

# Make another graphic, reversing the roles of age and sex.
fmodel(.___, .___)

```

*** =solution
# Construct the model
mod1 <- lm( wage ~ 1 + age + sex, data = CPS85)

# Make a graphic of mod1 with age on the x-axis and sex as color.
fmodel(mod1, ~ age + sex)

# Make another graphic, reversing the roles of age and sex.
fmodel(mod1, ~ sex + age)
```{r}

```

*** =sct
```{r}

# Final message the student will see upon completing the exercise
success_msg("Which graph do you find easier to interpret?")
```

